Coherent optical association of a single molecule -- Supplemental material

### 2020-11-05 paper.tex
Mention tweezer waist
Update on Overleaf.

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of Raman transition
    with loss on the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. % to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

>>>>

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of Raman transition
    with loss on the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
    which defines the location of the atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. % to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

### 2020-11-05 sm.tex
White space, regenerate PDF
Reproducible SM
[sm] todo
Update on Overleaf.

@@

%Add S to labels
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
\renewcommand{\thepage}{S\arabic{page}}  
\renewcommand{\thesection}{S\arabic{section}}   
\renewcommand{\theequation}{S.\arabic{equation}}

@@

@@

>>>>

\newcommand{\todo}[1]{}

@@

% Add S to labels
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S.\arabic{equation}}

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\hypersetup{
  pdfcreator={},
  pdfproducer={}
}
\fi

@@

For the purposes of this work, we denote $\Omega_a $($\Omega_m$) as the Rabi frequencies to drive a transition from the atom (target molecule) state to the intermediate state used in the Raman transition corresponding to the power in a single beam, $P_a$ ($P_m$). Thus, the Raman Rabi frequency remains $\Omega_a\Omega_m/2\Delta$. Cross coupling affects the scattering rate and light shift, and assuming equal powers in both beams, these quantities become $ \Gamma_e \Omega_m^2 / 2\Delta^2 + \Gamma_e \Omega_a^2 / 2\Delta^2 $ and $ \Omega_m^2/2\Delta - \Omega_a^2/2\Delta $, where $\Gamma_e$ is the excited state linewidth.

@@

\todo{
  Power/intensity calibration
}
